%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------
 
\documentclass{resume} % Use the custom resume.cls style 

\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Manoja Somarathna} % Your name 
\address{ Baththramulla,Colombo,10120,
 Sri Lanka} % Your address 
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional) 
\address{+94 742770633 \\ manojamsomarathna@gtmail.com} % Your phone number and email

\begin{document}  

%   SUMMARY
%--------------------------------------------------------------------------------

\begin{rSection}{  SUMMARY } \itemsep -3pt        

\item Motivated and detail-oriented Full Stack Web Developer with solid knowledge in both frontend and backend development. Skilled in HTML, CSS, JavaScript, React.js, Bootstrap, Tailwind, Java, Spring Boot, Node.js, Express.js, MySQL, and MongoDB. Experienced in building responsive, user-friendly web applications with RESTful APIs. Proficient in Git/GitHub, agile practices, and collaborative problem-solving. Seeking a Full Stack Web Developer Internship to apply technical skills and contribute to innovative projects.
  
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

{\bf  BSc (Hons) in Computing(Software engineering)} \hfill {March 2023 - March 2027}
\\ 
National Institute of Business Management(NIBM),
\\
Colombo 07


{\bf Higher National Diploma in Software Engineering} \hfill {March 2024 - April 2025}
\\ 
National Institute of Business Management


{\textbf{Diploma in Software Engineering}}  \hfill{March 2023 - March 2024}
\\
National Institute of Business Management
\\

{\bf   Relevant Coursework:}
Object-Oriented Programming, Data Structures and Algorithms, Database Management
 Systems, Software Engineering, Web Development, Computer Networks, Operating Systems, Information Systems Analysis and Design, Software Project Management
\\

  
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection} 

%----------------------------------------------------------------------------------------

%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
 Frontend:& HTML, CSS, JavaScript,TypeScript,Angular, React.js,Bootstrap, Tailwind CSS\\    
 
 Backend:&  Node.js, Java (Spring Boot)\\    

 Databases:&  MySQL, MongoDB, Firebase\\  

 API Development:&  REST API\\  

 Version Contro:&  Git, GitHub\\  

 Tools:&  Postman, IntelliJ IDEA, VS Code\\  

  Cloud  Deployment:&   AWS (EC2), Google Cloud
\\  
 
\end{tabular}   

\end{rSection}
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{skills and INTERESTS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Interests &  Reading
 Traveling
 Coding
 Learning New Programming
 Languages\\&
 Exploring Technology Trends
 \\    
 Soft Skills & Problem-Solving
 Time Management
 Communication Skills
 Adaptability\\&
 Continuous Learning\\     
 
\end{tabular}   

\end{rSection}

%-------------------------------------------------------------------------------
%	PROJECTS

\begin{rSection}{PROJECTS}

\begin{rSubsection}{ PlanMyTrip – AI Travel Planning App} {}{}{} 

 \item Android app with AI-driven budget management and personalized
 travel recommendations. Integrated Google Places API and Gemini
 API for destinations, local experiences, and cost estimates. Built with
 Kotlin/Java and Firebase. Future features: real-time expense
 tracking, collaborative planning, and booking integration.
 
\end{rSubsection}  

%------------------------------------------------

\begin{rSubsection}{Clinic Management System
\\} {}{}{} 

\item Android app with AI-driven budget management and personalized
 travel recommendations. Integrated Google Places API and Gemini
 API for destinations, local experiences, and cost estimates. Built with
 Kotlin/Java and Firebase. Future features: real-time expense
 tracking, collaborative planning, and booking integration.
 
\end{rSubsection}

%-------------------------------------------------


\begin{rSubsection}{ERP System }{}{}{}

\item  Complete ERP solution for customer and item management with
 reporting capabilities. Technologies: PHP, MySQL, Bootstrap,
 HTML, CSS, JS. Key features: customer/item registration,
 invoice/item reports, form validation, and responsive UI.
 

\end{rSubsection}

%-------------------------------------------------- 

\begin{rSubsection}{WorkNest – Service Booking Android App}{}{}{}    

\item  Connects users with local service providers (electricians, plumbers,
 etc.). Built with Android Studio, Java, Firebase. Features: user
 authentication, service browsing and booking, live location
 integration, booking management, and WhatsApp support

\end{rSubsection} 

\end{rSection} 

%--------------------------------------------------------------------------------------CERTIFICATES
%    
%--------------------------------------------------------------------------------------
\begin{rSection}{CERTIFICATES }\itemsep -3pt     

{\textbf{Oracle Cloud Infrastructure 2025 – AI Foundations Associate}\textit(Oracle University)\hfill Octomber 2025  

{\textbf{Basics and Structure of Java Programming}\textit(Alison)\hfill Octomber 2025 


{\textbf{Database Foundations – Final Exam}\textit(Oracle Academy)\hfill August 2024 
 
 
\end{rSection}
 
 %-----------------------------------------------------------------------------

%--------------------------------------------------------------------------------------
% Extra-Cirrucular
%--------------------------------------------------------------------------------------

\begin{rSection}{EXTRA CIRRUCULAR} \itemsep -2pt   

\begin{itemize}
 
\item Member - NIBM IT Club \textbf \hfill  
\item Volunteer – NIBM Events and Workshops\textbf \hfill  
\item Participant – NIBM Hackathons / CodeFests \textbf{} \hfill

\end{itemize}  


\end{rSection} 

%---------------------------------------------------------------------------------
%  DECLARATION
%--------------------------------------------------------------------------------

\begin{rSection}{ Declaration  } \itemsep -3pt        

\item I hereby declare that all the details furnished above are true to the best of my knowledge and belief.   
  
\end{rSection}
\end{document}
